Supplemental Materials, Methods and Results

### 2022-04-12 supp/Supplemental Materials and Methods.Rmd
Code fixes
Added a few shortcuts. One, no need to rerun code to sort out data in long format. So, added two output data loads. Added a new code chunk to extract unique species names and lat, longs for those species that will be used to extract climate data. Exported as Species_LatLong_pluHabitat

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = TRUE, message = FALSE, warning = FALSE, tidy = TRUE, fig.width = 10)
## numbers >= 10^5 will be denoted in scientific notation,		  ## numbers >= 10^5 will be denoted in scientific notation,
  ## and rounded to 2 digits		  ## and rounded to 2 digits
  options(digits = 2)
```

```{r packages_data, results='hide'}
##################################
# Clean workspace
##################################
    rm(list=ls())

@@

    # loading functions
    source("../R/functions.R")

##################################
# Load Data & Manipulate
##################################

@@

```{r datadescrp}
#####################################
# Data Descriptions and Exploration
#####################################

@@

    ## Tree data; also fix up some errors
    tree_data <-  data %>%
                  mutate(species_full = gsub("Chinemys reevesii", "Mauremys reevesii", species_full)) %>% 
                  mutate(species_full = gsub("Enithares sp", "Enithares ciliata", species_full)) %>%
                  mutate(habitat = ifelse(species_full == "Pungitius pungitius", "m", habitat))  %>%
                  mutate(habitat = ifelse(species_full == "Danio rerio", "f", habitat))  %>%
                  group_by(species_full)%>%
                  mutate(n = length(habitat)) %>%
                  dplyr::select(species_full,  habitat, n) %>% 
                  distinct(species_full, habitat, n)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = TRUE, message = FALSE, warning = FALSE, tidy = TRUE, fig.width = 10)
## numbers >= 10^5 will be denoted in scientific notation,		  ## numbers >= 10^5 will be denoted in scientific notation,
  ## and rounded to 2 digits		  ## and rounded to 2 digits
  options(digits = 2)

##################################
# Clean workspace
##################################
    rm(list=ls())

@@

    # loading functions
    source("../R/functions.R")
```

```{r packages_data, results='hide', eval = FALSE}
##################################
# Load Data & Manipulate
##################################

@@

```{r datadescrp}
#####################################
# Data Descriptions and Exploration
#####################################
data_long <- read.csv("../output/data/data_final_long.csv")
data_wide <- read.csv("../output/data/data_final_wide.csv")

@@

    ## Tree data; also fix up some errors
    tree_data <-  data_long %>%
                  mutate(species_full = gsub("Chinemys reevesii", "Mauremys reevesii", species_full)) %>% 
                  mutate(species_full = gsub("Enithares sp", "Enithares ciliata", species_full)) %>%
                  mutate(habitat = ifelse(species_full == "Pungitius pungitius", "m", habitat))  %>%
                  mutate(habitat = ifelse(species_full == "Danio rerio", "f", habitat))  %>%
                  group_by(species_full)%>%
                  mutate(n = length(habitat)) %>%
                  dplyr::select(species_full,  habitat, n) %>% 
                  distinct(species_full, habitat, n)

    # Get the unique species lat and long data which will be used to extract climate data for each ppulation / species for wild derived sources.
    climate_data <-  data_long %>%
                  mutate(species_full = gsub("Chinemys reevesii", "Mauremys reevesii", species_full)) %>% 
                  mutate(species_full = gsub("Enithares sp", "Enithares ciliata", species_full)) %>%
                  mutate(habitat = ifelse(species_full == "Pungitius pungitius", "m", habitat))  %>%
                  mutate(habitat = ifelse(species_full == "Danio rerio", "f", habitat))  %>%
                  group_by(species_full)%>%
                  mutate(n = length(habitat)) %>%
                  dplyr::select(species_full,  habitat, source, n, lat, long) %>% 
                  distinct(species_full, habitat, n, source, lat, long) 
      write.csv(climate_data, file = "../data/climate_data/Species_LatLong_plusHabitat.csv", row.names=FALSE)
